Variable creation ObjectInAction

### 2020-07-06 Variable creation.Rmd
Cleaned file i-o

#Load packages
```{r}
library(nlme)
library(haven)
library(devtools)
library(psych)
library(mosaic)
library(tidyr)
library(dplyr)
library(irr)
select <- dplyr::select
```

Load data
```{r}
#clark
clark_measures <- read_spss("Raw data/Clark College Relationships Data/College_Relationship_Measures_1.sav")
clark_pairwise <- read_spss("Raw data/Clark College Relationships Data/College_Relationship_Pairwise_1.sav")

@@

Clark Scale Scores--creating scale scores for the Clark data.
```{r}
#SOO -- subtract internal SOO from external SOO
clark_measures$extSOO <- rowMeans(dplyr::select(clark_measures, otherint_1, otherint_2, otherint_5, otherint_6, otherint_10), na.rm=TRUE) #get average

clark_measures$intSOO <- rowMeans(dplyr::select(clark_measures, otherint_3, otherint_4, otherint_7, otherint_8, otherint_9, otherint_11, otherint_12), na.rm=TRUE) #get average

@@

#Meta SOO--subtract internal from external
clark_measures$extmetaSOO <- rowMeans(dplyr::select(clark_measures, metaint_1, metaint_2, metaint_5, metaint_6, metaint_10), na.rm=TRUE)

clark_measures$intmetaSOO <- rowMeans(dplyr::select(clark_measures, metaint_3, metaint_4, metaint_7, metaint_8, metaint_9, metaint_11, metaint_12), na.rm=TRUE)

@@

#Interaction Authenticity
clark_measures$authenticity <- rowMeans(dplyr::select(clark_measures, inter_1, inter_3, inter_5, inter_6, inter_7, inter_9, inter_10, interaux_5, interaux_6))

#SSO--average of how body 1 and how body 2
clark_measures <- clark_measures %>%
  mutate(howbody_avg = (howbody_1+howbody_2)/2)

@@

clark_measures$relag <- rowMeans(dplyr::select(clark_measures, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))

@@

clark_measures$careerasp <- rowMeans(dplyr::select(clark_measures, careerasp_1, careerasp_2, careerasp_3, careerasp4.r, careerasp_5, careerasp_6, careerasp7.r, careerasp_8, careerasp_9, careerasp10.r))

#TSO--subtract internal from external, multiply by -1
clark_measures$funcTSO <- rowMeans(dplyr::select(clark_measures,tso_1, tso_2, tso_4, tso_7, tso_9))
clark_measures$physTSO <- rowMeans(dplyr::select(clark_measures, tso_3, tso_5, tso_6, tso_8, tso_10))

clark_measures$TSO <- clark_measures$physTSO - clark_measures$funcTSO
clark_measures$TSO <- clark_measures$TSO*(-1)
```

SMITH SCALE SCORES
```{r}
smith <- smith %>%
  arrange(dyadID) %>%
  filter(dyadID!=16, !is.na(dyadID), dyadID!=798797, dyadID!=999, dyadID!=999999, dyadID!=9999) #filter out dyads with no data

#SOO
smith$extSOO <- rowMeans(dplyr::select(smith, otherint_1, otherint_2, otherint_5, otherint_6, otherint_10), na.rm=TRUE)

smith$intSOO <- rowMeans(dplyr::select(smith, otherint_3, otherint_4, otherint_7, otherint_8, otherint_9, otherint_11, otherint_12), na.rm=TRUE)

@@

#Meta SOO
smith$extmetaSOO <- rowMeans(dplyr::select(smith, metaint_1, metaint_2, metaint_5, metaint_6, metaint_10), na.rm=TRUE)

smith$intmetaSOO <- rowMeans(dplyr::select(smith, metaint_3, metaint_4, metaint_7, metaint_8, metaint_9, metaint_11, metaint_12), na.rm=TRUE)

@@

#Interaction Authenticity
smith$authenticity <- rowMeans(dplyr::select(smith, inter_1, inter_3, inter_5, inter_6, inter_7, inter_9, inter_10, interaux_5, interaux_6))

#SSO
smith <- smith %>%
  mutate(howbody_avg = (howbody_1+howbody_2)/2)

@@

smith$relag <- rowMeans(dplyr::select(smith, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9.r))

@@

smith$careerasp <- rowMeans(dplyr::select(smith, careerasp_1, careerasp_2, careerasp_3, careerasp4.r, careerasp_5, careerasp_6, careerasp7.r, careerasp_8, careerasp_9, careerasp10.r))

#TSO
smith$funcTSO <- rowMeans(dplyr::select(smith,tso_1, tso_2, tso_4, tso_7, tso_9))
smith$physTSO <- rowMeans(dplyr::select(smith, tso_3, tso_5, tso_6, tso_8, tso_10))

smith$TSO <- smith$physTSO-smith$funcTSO
smith$TSO <- smith$TSO*-1

#Write out csv with created variables
write.csv(clark_measures, "Cleaned data/clark_measures.csv")
write.csv(smith, "Cleaned data/smith.csv")
```

Trigrams
```{r}
###Clark
#Eliminate unnecessary columns
trigram_check <- trigram_check[,1:8]

@@

#create a correct trigram score for each participant
trigram_clark <- trigram_check %>%
  group_by(partID) %>%
  summarise(trigram_score = sum(trigram_correct)) %>%
  dplyr::select(partID, trigram_score)

@@

```{r}
###SMITH
#select only trigram related variables
smith_trigrams <- smith %>%
  dplyr::select(partID, dyadID, rat1_1.0, rat2_1.0,rat3_1.0, rat4_1.0,rat5_1.0, rat6_1.0, rat7_1.0, rat8_1.0, rat9_1.0, rat10_1) %>%
  arrange(dyadID, partID)

smith_trigrams_long <- gather(smith_trigrams, trigram, response, rat1_1.0:rat10_1)

#change trigram from generic name to the specific trigram
smith_trigrams_long <- smith_trigrams_long %>%
  mutate(trigram = ifelse(trigram=="rat1_1.0", "QUACK:POND:WADDLE",
                          ifelse(trigram=="rat2_1.0", "ATHLETES:WEB:RABBIT",
                                 ifelse(trigram=="rat3_1.0", "HONEY:SWARM:STING",
                                        ifelse(trigram=="rat4_1.0", "MATCHES:SMOKE:BUSH",
                                               ifelse(trigram=="rat5_1.0", "CHOCOLATE:FORTUNE:TIN",
                                                      ifelse(trigram=="rat6_1.0", "CURIOSITY:NAP:WHISKERS",
                                                             ifelse(trigram=="rat7_1.0", "STALK:TRAINER:KING",
                                                                    ifelse(trigram=="rat8_1.0", "SURPRISE:LINE:BIRTHDAY",
                                                                           ifelse(trigram=="rat9_1.0", "RED:GO:CAR", 
                                                                                  ifelse(trigram=="rat10_1", "MOUSE : SHARP : BLUE", NA)))))))))))

#create a correct response column
smith_trigrams_long <- smith_trigrams_long %>%
  mutate(correct_response=ifelse(trigram=="QUACK:POND:WADDLE", "Duck",
                          ifelse(trigram=="ATHLETES:WEB:RABBIT", "Foot",
                                 ifelse(trigram=="HONEY:SWARM:STING","Bee",
                                        ifelse(trigram=="MATCHES:SMOKE:BUSH", "Fire", 
                                               ifelse(trigram=="CHOCOLATE:FORTUNE:TIN", "Cookie",
                                                      ifelse(trigram=="CURIOSITY:NAP:WHISKERS","Cat",
                                                             ifelse(trigram=="STALK:TRAINER:KING","Lion",
                                                                    ifelse(trigram=="SURPRISE:LINE:BIRTHDAY", "Party",
                                                                           ifelse(trigram=="RED:GO:CAR", "Stop",
                                                                                  ifelse(trigram=="MOUSE : SHARP : BLUE", "Cheese", NA))))))))))) %>%
  arrange(partID, dyadID)

smith_trigrams_long <- smith_trigrams_long[,c(1,2,3,5,4)]

@@

#Summarize a final correct trigram
smith_triscore <- smith_trigrams_graded %>%
  group_by(partID, dyadID) %>%
  summarise(trigram_score=sum(final_correct))%>%
  dplyr::select(partID, dyadID, trigram_score)

@@

sexist sentences
```{r}
#Calculate ICC score to see if we can average
clark_sentences <- clark_sentences[,1:8]

@@

@@

#Creating sexist sentence file
smith$dyadID <- as.numeric(smith$dyadID)
smith$partID <- as.numeric(smith$partID)
smith_sentences_long <- smith %>%
  #remove dyads with no data
  filter(dyadID!=16, !is.na(dyadID), dyadID!=798797, dyadID!=999, dyadID!=999999, dyadID!=9999) %>%
  #select just sexism related variables
  select(partID, dyadID, sexismpre_1:sexismpre_8) %>%
  arrange(dyadID)

#make data long
smith_sentences_long <- gather(smith_sentences_long, sentence, target, sexismpre_1:sexismpre_8)

#create a column with the actual sentence as well as a sentence number column
smith_sentences_long <- smith_sentences_long %>%
  mutate(stem=ifelse(sentence=="sexismpre_1", "Linda swatted at the flies", 
                     ifelse(sentence=="sexismpre_2", "Helen crammed for the test",
                            ifelse(sentence=="sexismpre_3", "Shirley asked for help getting home",
                                   ifelse(sentence=="sexismpre_4", "Sam read the newspaper",
                                          ifelse(sentence=="sexismpre_5", "Jenny went home to cook dinner",
                                                 ifelse(sentence=="sexismpre_6", "Katherine baby-sat the neighbor's kids",
                                                        ifelse(sentence=="sexismpre_7", "Tom bottle fed the baby",
                                                               ifelse(sentence=="sexismpre_8", "Bert changed the oil", NA))))))))) %>%
    mutate(sentence=ifelse(sentence=="sexismpre_1", 1, 
                     ifelse(sentence=="sexismpre_2", 2,
                            ifelse(sentence=="sexismpre_3", 3,
                                   ifelse(sentence=="sexismpre_4", 4,
                                          ifelse(sentence=="sexismpre_5", 5,
                                                 ifelse(sentence=="sexismpre_6", 6,
                                                        ifelse(sentence=="sexismpre_7", 7,
                                                               ifelse(sentence=="sexismpre_8", 8, NA)))))))))

#change order of sentences
smith_sentences_long <- smith_sentences_long[,c(1,2,3,5,4)]

#remove rows with no target data
smith_sentences_long <- smith_sentences_long %>%
  filter(target!="") %>%
  arrange(dyadID, partID)

@@

#Read in coded sentences, code correlations
kat_codes <- read.csv("Raw data/Smith College Relationships Data/kat_recode.csv")

xinyu_codes <- read.csv("Raw data/Smith College Relationships Data/xinyu_recode.csv")

>>>>

#Load packages
```{r}
library(nlme)
library(haven)
library(devtools)
library(psych)
library(mosaic)
library(tidyr)
library(irr)
library(dplyr)
```

#Load data
```{r}
#clark
clark_measures <- read_spss("Raw data/Clark College Relationships Data/College_Relationship_Measures_1.sav")
clark_pairwise <- read_spss("Raw data/Clark College Relationships Data/College_Relationship_Pairwise_1.sav")

@@

#Scale Scores

Creating scale scores for the Clark data.

```{r}
#SOO -- subtract internal SOO from external SOO
clark_measures$extSOO <- rowMeans(select(clark_measures, otherint_1, otherint_2, 
                                         otherint_5, otherint_6, otherint_10), na.rm=TRUE) #get average

clark_measures$intSOO <- rowMeans(select(clark_measures, otherint_3, otherint_4, 
                                         otherint_7, otherint_8, otherint_9, 
                                         otherint_11, otherint_12), na.rm=TRUE) #get average

@@

#Meta SOO--subtract internal from external
clark_measures$extmetaSOO <- rowMeans(select(clark_measures, metaint_1, metaint_2, 
                                             metaint_5, metaint_6, metaint_10), na.rm=TRUE)

clark_measures$intmetaSOO <- rowMeans(select(clark_measures, metaint_3, metaint_4, 
                                             metaint_7, metaint_8, metaint_9, 
                                             metaint_11, metaint_12), na.rm=TRUE)

@@

#Interaction Authenticity
clark_measures$authenticity <- rowMeans(select(clark_measures, inter_1, inter_3, 
                                               inter_5, inter_6, inter_7, inter_9, 
                                               inter_10, interaux_5, interaux_6), na.rm=TRUE)

#SSO--average of how body 1 and how body 2
clark_measures$howbody_avg <- rowMeans(select(clark_measures, howbody_1, howbody_2), na.rm=TRUE)

@@

clark_measures$relag <- rowMeans(select(clark_measures, relag_1, relag_2, 
                                        relag_3, relag_4, relag_5, relag_6, 
                                        relag_7, relag_8, relag_9.r), na.rm=TRUE)

@@

clark_measures$careerasp <- rowMeans(select(clark_measures, careerasp_1, careerasp_2, 
                                            careerasp_3, careerasp4.r, careerasp_5, 
                                            careerasp_6, careerasp7.r, careerasp_8, 
                                            careerasp_9, careerasp10.r), na.rm=TRUE)

#TSO--subtract internal from external, multiply by -1
clark_measures$funcTSO <- rowMeans(select(clark_measures,tso_1, tso_2, tso_4, tso_7, tso_9), na.rm=TRUE)
clark_measures$physTSO <- rowMeans(select(clark_measures, tso_3, tso_5, tso_6, tso_8, tso_10), na.rm=TRUE)

clark_measures$TSO <- (clark_measures$physTSO - clark_measures$funcTSO)*(-1)
```

Creating scale scores for the Smith data.

```{r}
smith <- smith %>%
  arrange(dyadID) %>%
  filter(dyadID!=16, !is.na(dyadID), dyadID!=798797, 
         dyadID!=999, dyadID!=999999, dyadID!=9999) #filter out dyads with no data
```

```{r}
#SOO
smith$extSOO <- rowMeans(select(smith, otherint_1, otherint_2, 
                                otherint_5, otherint_6, otherint_10), na.rm=TRUE)

smith$intSOO <- rowMeans(select(smith, otherint_3, otherint_4, 
                                otherint_7, otherint_8, otherint_9, 
                                otherint_11, otherint_12), na.rm=TRUE)

@@

#Meta SOO
smith$extmetaSOO <- rowMeans(select(smith, metaint_1, metaint_2, 
                                    metaint_5, metaint_6, metaint_10), na.rm=TRUE)

smith$intmetaSOO <- rowMeans(select(smith, metaint_3, metaint_4, 
                                    metaint_7, metaint_8, metaint_9, 
                                    metaint_11, metaint_12), na.rm=TRUE)

@@

#Interaction Authenticity
smith$authenticity <- rowMeans(select(smith, inter_1, inter_3, inter_5, 
                                      inter_6, inter_7, inter_9, inter_10, 
                                      interaux_5, interaux_6), na.rm=TRUE)

#SSO
smith$howbody_avg <- rowMeans(select(smith, howbody_1, howbody_2), na.rm=TRUE)

@@

smith$relag <- rowMeans(select(smith, relag_1, relag_2, relag_3, 
                               relag_4, relag_5, relag_6, relag_7, 
                               relag_8, relag_9.r), na.rm=TRUE)

@@

smith$careerasp <- rowMeans(select(smith, careerasp_1, careerasp_2, 
                                   careerasp_3, careerasp4.r, careerasp_5, 
                                   careerasp_6, careerasp7.r, careerasp_8, 
                                   careerasp_9, careerasp10.r), na.rm=TRUE)

#TSO
smith$funcTSO <- rowMeans(select(smith,tso_1, tso_2, tso_4, tso_7, tso_9), na.rm=TRUE)
smith$physTSO <- rowMeans(select(smith, tso_3, tso_5, tso_6, tso_8, tso_10), na.rm=TRUE)

smith$TSO <- (smith$physTSO - smith$funcTSO)*(-1)
```

Step not needed...processing continues
```{r}
#Write out csv with created variables
#write.csv(clark_measures, "Cleaned data/clark_measures.csv")
#write.csv(smith, "Cleaned data/smith.csv")
```

#Trigrams

Clark

```{r}
###Clark
#Eliminate unnecessary columns
trigram_check <- trigram_check[,1:8]

@@

#create a correct trigram score for each participant
trigram_clark <- trigram_check %>%
  group_by(partID) %>%
  summarise(trigram_score = sum(trigram_correct)) %>%
  select(partID, trigram_score)

@@

Smith

```{r}
###SMITH

#comented code here used only ONCE to grade trigrams...graded trigrams file is read in at the bottom of this chunk

#select only trigram related variables
# smith_trigrams <- smith %>%
#   select(partID, dyadID, rat1_1.0, rat2_1.0,rat3_1.0, rat4_1.0,
#          rat5_1.0, rat6_1.0, rat7_1.0, rat8_1.0, rat9_1.0, rat10_1) %>%
#   arrange(dyadID, partID)
# 
# smith_trigrams_long <- gather(smith_trigrams, trigram, response, rat1_1.0:rat10_1)
# 
# #change trigram from generic name to the specific trigram
# smith_trigrams_long <- smith_trigrams_long %>%
#   mutate(trigram = ifelse(trigram=="rat1_1.0", 
#                           "QUACK:POND:WADDLE",
#                           ifelse(trigram=="rat2_1.0", 
#                                  "ATHLETES:WEB:RABBIT",
#                                  ifelse(trigram=="rat3_1.0", 
#                                         "HONEY:SWARM:STING",
#                                         ifelse(trigram=="rat4_1.0", 
#                                                "MATCHES:SMOKE:BUSH",
#                                                ifelse(trigram=="rat5_1.0", 
#                                                       "CHOCOLATE:FORTUNE:TIN",
#                                                       ifelse(trigram=="rat6_1.0", 
#                                                              "CURIOSITY:NAP:WHISKERS",
#                                                              ifelse(trigram=="rat7_1.0", 
#                                                                     "STALK:TRAINER:KING",
#                                                                     ifelse(trigram=="rat8_1.0", 
#                                                                            "SURPRISE:LINE:BIRTHDAY",
#                                                                            ifelse(trigram=="rat9_1.0", 
#                                                                                   "RED:GO:CAR", 
#                                                                                   ifelse(trigram=="rat10_1", 
#                                                                                          "MOUSE : SHARP : BLUE", 
#                                                                                          NA)))))))))))
# 
# #create a correct response column
# smith_trigrams_long <- smith_trigrams_long %>%
#   mutate(correct_response=ifelse(trigram=="QUACK:POND:WADDLE", 
#                                  "Duck",
#                           ifelse(trigram=="ATHLETES:WEB:RABBIT", 
#                                  "Foot",
#                                  ifelse(trigram=="HONEY:SWARM:STING",
#                                         "Bee",
#                                         ifelse(trigram=="MATCHES:SMOKE:BUSH", 
#                                                "Fire", 
#                                                ifelse(trigram=="CHOCOLATE:FORTUNE:TIN", 
#                                                       "Cookie",
#                                                       ifelse(trigram=="CURIOSITY:NAP:WHISKERS",
#                                                              "Cat",
#                                                              ifelse(trigram=="STALK:TRAINER:KING",
#                                                                     "Lion",
#                                                                     ifelse(trigram=="SURPRISE:LINE:BIRTHDAY", 
#                                                                            "Party",
#                                                                            ifelse(trigram=="RED:GO:CAR", 
#                                                                                   "Stop",
#                                                                                   ifelse(trigram=="MOUSE : SHARP : BLUE", 
#                                                                                          "Cheese", 
#                                                                                          NA))))))))))) %>%
#   arrange(partID, dyadID)
# 
# smith_trigrams_long <- smith_trigrams_long[,c(1,2,3,5,4)]

@@

#Summarize a final correct trigram
smith_triscore <- smith_trigrams_graded %>%
  group_by(partID, dyadID) %>%
  summarise(trigram_score=sum(final_correct))%>%
  select(partID, dyadID, trigram_score)

@@

#Sexist Sentences

Clark

```{r}
#Calculate ICC score to see if we can average
clark_sentences <- clark_sentences[,1:8]

@@

Smith

@@

#comented code here used only ONCE to code sentences...graded trigrams file is read in at the bottom of this chunk

#Creating sexist sentence file
# smith$dyadID <- as.numeric(smith$dyadID)
# smith$partID <- as.numeric(smith$partID)
# smith_sentences_long <- smith %>%
#   #remove dyads with no data
#   filter(dyadID!=16, !is.na(dyadID), dyadID!=798797, dyadID!=999, dyadID!=999999, dyadID!=9999) %>%
#   #select just sexism related variables
#   select(partID, dyadID, sexismpre_1:sexismpre_8) %>%
#   arrange(dyadID)
# 
# #make data long
# smith_sentences_long <- gather(smith_sentences_long, sentence, target, sexismpre_1:sexismpre_8)
# 
# #create a column with the actual sentence as well as a sentence number column
# smith_sentences_long <- smith_sentences_long %>%
#   mutate(stem=ifelse(sentence=="sexismpre_1", 
#                      "Linda swatted at the flies", 
#                      ifelse(sentence=="sexismpre_2", 
#                             "Helen crammed for the test",
#                             ifelse(sentence=="sexismpre_3", 
#                                    "Shirley asked for help getting home",
#                                    ifelse(sentence=="sexismpre_4", 
#                                           "Sam read the newspaper",
#                                           ifelse(sentence=="sexismpre_5", 
#                                                  "Jenny went home to cook dinner",
#                                                  ifelse(sentence=="sexismpre_6", 
#                                                         "Katherine baby-sat the neighbor's kids",
#                                                         ifelse(sentence=="sexismpre_7", 
#                                                                "Tom bottle fed the baby",
#                                                                ifelse(sentence=="sexismpre_8", 
#                                                                       "Bert changed the oil", NA))))))))) %>%
#     mutate(sentence=ifelse(sentence=="sexismpre_1", 1, 
#                      ifelse(sentence=="sexismpre_2", 2,
#                             ifelse(sentence=="sexismpre_3", 3,
#                                    ifelse(sentence=="sexismpre_4", 4,
#                                           ifelse(sentence=="sexismpre_5", 5,
#                                                  ifelse(sentence=="sexismpre_6", 6,
#                                                         ifelse(sentence=="sexismpre_7", 7,
#                                                                ifelse(sentence=="sexismpre_8", 8, NA)))))))))
# 
# #change order of sentences
# smith_sentences_long <- smith_sentences_long[,c(1,2,3,5,4)]
# 
# #remove rows with no target data
# smith_sentences_long <- smith_sentences_long %>%
#   filter(target!="") %>%
#   arrange(dyadID, partID)

@@

#Read in coded sentences, code correlations
kat_codes <- read.csv("Raw data/Smith College Relationships Data/kat_recode.csv")
xinyu_codes <- read.csv("Raw data/Smith College Relationships Data/xinyu_recode.csv")
